Intentional release of native species undermines ecological stability

### 2022-10-03 rmd/supporting_info.Rmd
Update supporting_info.Rmd

As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario. In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community. The rest of the simulation procedure is identical to the two-species model. We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).

@@

The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release. The left column in **Figure S**\@ref(fig:fig-2sp-w)A) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`). For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics. In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-s)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)). However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).

>>>>

As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario. In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community. In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct". The rest of the simulation procedure is identical to the two-species model. We summarized values of simulation parameters in **Table S**\@ref(tab:tab-para).

@@

The analysis of a two-species community revealed the distinct parameter space predicting a stabilizing, neutral, or destabilizing effect of intentional release. The left column in **Figure S**\@ref(fig:fig-2sp-w)**A**) shows the predictions in scenarios with no environmental stochasticity ($\sigma_{\varepsilon} =$ `r min(list_param[[1]]$sd_env)`) and weak competition ($\bar{\alpha}=$ `r min(list_param[[1]]$alpha)`). For lower values of intrinsic growth rate $r_i$ ($<1.5$), intentional release had neutral (with higher $K$) to destabilizing effects (with lower $K$) on community dynamics. In the meantime, stabilization with intentional release occurred for higher values of $r_i$ ($\ge 1.5$) by dampening limit cycles or chaos (**Figure S**\@ref(fig:fig-2sp-s)), which is reflected in decreased SD $\sigma$ (**Figure S**\@ref(fig:fig-2sp-w)). However, the long-term mean of community density $\mu$ consistently decreased with intentional release in almost all cases except for only a few combinations of $r_i$ and $K$ (**Figure S**\@ref(fig:fig-2sp-w)).
